---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Data processing"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(janitor) # for clean_names()
library(stringr)
library(kableExtra)

```

# Get data

```{r}

# demographics
data_demographics_raw <- read_csv("../../implicit evaluations study/data/raw/data_demographics_raw.csv") |>
  janitor::clean_names()

# data_demographics_raw_messy <- read_csv("../../../data/AMP study/raw/data_demographics_raw_messy.csv", skip = 2) |>
#   janitor::clean_names()

# self report measure
data_selfreport_raw <- read_csv("../../implicit evaluations study/data/raw/data_selfreport_raw.csv") |>janitor::clean_names()

# affect attribution procedure
data_amp_raw <- read_csv("../../implicit evaluations study/data/raw/data_amp_raw.csv") |>
  janitor::clean_names()

```

# Demographics

```{r}

dat_age_gender <- data_demographics_raw |>
  select(subject, date, time, trialcode, response) |>
  pivot_wider(names_from = trialcode,
              values_from = response) |>
  mutate(gender = tolower(gender),
         gender = stringr::str_remove_all(gender, regex("\\W+")), # regex is both very useful and awful to write
         gender = case_when(gender == "female" ~ gender,
                            gender == "male" ~ gender,
                            gender == "nonbinary" ~ gender,
                            gender == "woman" ~ "female",
                            gender == "man" ~ "male",
                            TRUE ~ "other/missing/error"),
         age = case_when(str_detect(age, "^[0-9]+$") ~ age, # if the value is only numbers, keep it. 
                         TRUE ~ "other/missing/error")) 

```

# Exclusions / data quality

## AMP

```{r}

data_amp_performance_criteria <- data_amp_raw |> 
  filter(blockcode != "practice", 
         trialcode != "instructions") |> 
  mutate(latency_prob = if_else(latency < 100, TRUE, FALSE)) |> 
  group_by(subject) |> 
  summarize(proportion_fast_trials_amp = mean(latency_prob)) |>
  mutate(exclude_amp_performance = ifelse(proportion_fast_trials_amp > 0.10, "exclude", "include"))

```

## Self-reports

```{r}

# trial level data
data_selfreport_trial_level <- data_selfreport_raw |>
  select(subject, trialcode, response) |>
  filter(trialcode %in% c("like", "prefer", "positive")) |>
  rename(item = trialcode) |>
  filter(response != "Ctrl+'B'") |>
  mutate(response = as.numeric(response))

# mean scored
data_selfreport_mean_score <- data_selfreport_trial_level |>
  group_by(subject) |>
  summarize(mean_evaluation = mean(response, na.rm = TRUE))

# combined
data_selfreport_scored <- 
  full_join(data_selfreport_trial_level |>
              pivot_wider(names_from = "item",
                          values_from = "response"),
            data_selfreport_mean_score,
            by = "subject")

```

# Affect Misattribution Procedure

TODO extract evaluations on the AMP test blocks and convert to an overall bias score

```{r}


```

# Combine

```{r}

# combine all dfs created in the previous chunks
data_processed_temp <- dat_age_gender |>
  full_join(data_selfreport_scored, by = "subject") |> 
  full_join(data_amp_performance_criteria, by = "subject")

# flag all subjects with more than one row in the wide-format data. these should be excluded in the analysis.
# a more elaborate approach would be to track down the individual dupicate cases and determine which of the mulitiple cases should be retained. 
data_processed_duplicates <- data_processed_temp |>
  count(subject) |>
  mutate(exclude_duplicate_data = if_else(n > 1, "exclude", "include")) |>
  select(-n)

# join in the duplicates df
data_processed_before_exclusions <- data_processed_temp |>
  full_join(data_processed_duplicates, by = "subject")

```

# Define master exclusions
##Demographics
```{r}

# create a master exclude_participant variable
data_processed <- data_processed_before_exclusions |>
  mutate(exclude_participant = case_when(tolower(age) == "test" ~ "exclude",
                                         tolower(gender) == "test" ~ "exclude",
                                         is.na(mean_evaluation) ~ "exclude",
                                         # in this case we will exclude participants with missing demographics data or outcomes measures data. 
                                         # Note that "list-wise exclusions" like this aren't always justified, as missingness often isn't at random. 
                                         # How to treat missing data is a  whole area of work in itself, which we wont cover here.
                                         is.na(age) ~ "exclude", 
                                         is.na(gender) ~ "exclude",
                                         exclude_amp_performance == "exclude" ~ "exclude",
                                         exclude_duplicate_data == "exclude" ~ "exclude",
                                         TRUE ~ "include"))

```

##WEEK7 Selfreports
- Add exclusions for data completeness for the self reports. i.e., master exclude variable should also be set to "exclude" if they don't have responses for the three individual self report item.

### just data_selfreport_scored
I wasn't sure which of the data sets to take, so I made two versions where I exclude the data. 
Both are pretty the same.
``` {r}

#I don't know if that will make the process easier for you, but you can also read in the finished datasets otherwise
data_selfreport_scored_exclusions <- read_csv("../../implicit evaluations study/data/week7/data_selfreport_scored_exclusions.csv")


data_selfreport_scored_exclusions <- data_selfreport_scored|>
  mutate(exclude_participant = case_when(is.na(positive) ~ "exclude",
                                         is.na(prefer) ~ "exclude",     
                                         is.na(like) ~ "exclude",
                                         is.na(mean_evaluation) ~ "exclude",
                                         TRUE ~ "include"))

#for me to look at the stuff

#data_selfreport_scored|>
#  count(like)
#  count(prefer) <- hat ein NA
#    count(positive) <- hat ein NA
#    count(mean_evaluation)
#  count(subject) |>
#  mutate(exclude_duplicate_data = if_else(n > 1, "exclude", "include"))|>  # --> no duplicates
#  kable() |>
#  kable_classic(full_width = FALSE)


#write_csv(data_selfreport_scored_exclusions, "../../implicit evaluations study/data/week7/data_selfreport_scored_exclusions.csv")

```

### combined data_selfreport
Both approaches exclude the same people, it is basically the same, only this dataset is formatted differently and has additional information.
``` {r}

data_selfreport_exclusions <- read_csv("../../implicit evaluations study/data/week7/data_selfreport_exclusions.csv")


#preparation - need this for the full_join!
#practically the same as before, only I have selected 3 column
data_selfreport_scored_to_combine <- data_selfreport_scored|>
  mutate(ex_clude_participant = case_when(is.na(positive) ~ "exclude",
                                         is.na(prefer) ~ "exclude",     
                                         is.na(like) ~ "exclude",
                                         is.na(mean_evaluation) ~ "exclude",
                                         TRUE ~ "include"))|>
  select(subject, mean_evaluation, ex_clude_participant)



#Preparation
data_selfreport_raw_exclusions <- data_selfreport_raw|>
  filter(trialcode %in% c("like", "prefer", "positive"),
         response != "Ctrl+'B'")|>
  rename(item = trialcode) |>
  mutate(response = as.numeric(response))


data_selfreport_exclusions <- full_join(data_selfreport_raw_exclusions,
                                        data_selfreport_scored_to_combine
                                        ,  by = "subject")|>
  mutate(exclude_participant = case_when(is.na(response) ~ "exclude", #actually not necassary lol
                                        ex_clude_participant == "exclude" ~ "exclude",
                                         TRUE ~ "include"))|>
  select(-ex_clude_participant)



#all Participants have tree responses, except the one
table(data_selfreport_exclusions$subject)|>
    kable() |>
  kable_classic(full_width = FALSE)


#write_csv(data_selfreport_exclusions, "../../implicit evaluations study/data/week7/data_selfreport_exclusions.csv")

```


##WEEK7 AMP
- Add exclusions for the AMP task. It should have the "correct" number of trials. 
 I think it's 72 :) (with practice -> 82)
How to know what number is the correct number of trials? Think about how to explore this in your data with code. Write a very brief description of what you tried, what worked or didn't, and what you decided was the correct number of trials as a response to this assignment. 
``` {r}

data_amp_after_exclude <- read_csv("../../implicit evaluations study/data/week7/data_amp_after_exclude.csv") |>
  select(-1) 

#Instead of a full_join with data_amp_raw and data_amp_performance_criteria, I made a new dataset
#I could have excluded more columns, but wasn't sure if we could still use them later, so some "selects" are with #.
data_amp_before_exclude <- data_amp_raw|>
  filter(blockcode != "practice", trialcode != "instructions") |> 
  mutate(latency_prob = if_else(latency < 100, TRUE, FALSE),
         proportion_fast_trials_amp = mean(latency_prob, .by = subject),
         exclude_amp_performance = ifelse(proportion_fast_trials_amp > 0.10, "exclude", "include"), .by = subject) |>
  select(-blockcode) #-primestim, -targetstim


#the count of how many Trials are necessary
participant_count <- table(data_amp_before_exclude$subject)


#excluded also the duplicate!
data_amp_after_exclude <- data_amp_before_exclude|>
     mutate(participant_count = participant_count[as.character(subject)], 
            exclude_participant = case_when(exclude_amp_performance == "exclude" ~ "exclude",
                                            participant_count < 72  ~ "exclude",
                                            participant_count > 72  ~ "exclude",
                                            TRUE ~ "include"))


#count trials without practice  
table(data_amp_before_exclude$subject)  |>
  kable() |>
  kable_classic(full_width = FALSE)

#count trial with practice
#table(data_amp_raw$subject)  |>
#  kable() |>
#  kable_classic(full_width = FALSE)

#a diffrent attempt to count, but practicly the same
#data_amp_before_exclude|>
#  count(subject)|>
#  kable() |>
#  kable_classic(full_width = FALSE)

#just looking on numbers :) 2_73
#data_amp_after_exclude|>
#  count(blocknum_and_trialnum)

# ... an attempt, but not relly a smart attempt
#data_amp_before_exclude |>
#  select(subject, blocknum_and_trialnum) |>
#  pivot_wider(names_from = blocknum_and_trialnum,
#              values_from = subject)  |>
#    kable() |>
#  kable_classic(full_width = FALSE)


#write.csv(data_amp_after_exclude,"../../implicit evaluations study/data/week7/data_amp_after_exclude.csv")


```

# Write to disk

```{r}

# in case this dir doesn't exist, create it
dir.create("../../../data/AMP study/processed/")

# save data to disk in that dir
write_csv(data_processed, "../../../data/AMP study/processed/data_processed.csv")

```

# Session info

```{r}

sessionInfo()

```


