---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Analysis"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

# set knit options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Dependencies

```{r}

library(tidyverse)
library(knitr)
library(kableExtra)
library(janitor)
library(scales)

library("ggExtra")
library("ggplot2")
library("viridis") 
library("ggsci")
library(ggrepel)
library(ggmagnify)
library(ggridges)
library(patchwork)
library(easystats)
library(psych)


```
#SET.SEED

```{r}
set.seed(123) 

```

# Data

Load the processed data and apply the global exclusions.

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv")

data_processed_after_exclusions <- data_processed |>
  filter(exclude_participant == "include")

```

# Sample descriptives

## Sample size before exclusions

```{r}

data_processed |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("Whole sample" = 1)) |> # note that you can add header rows to tables like this. The "1" indicates the number of columns the header should span. The sum of these numbers must equal the number of columns or you'll get an error.
  kable_classic(full_width = FALSE)

```

## Sample size after exclusions

Sample used in subsequent analyses

```{r}

data_processed_after_exclusions |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("For analysis" = 1)) |>
  kable_classic(full_width = FALSE)

```

## Age

```{r}

data_processed_after_exclusions |>
  mutate(age = as.numeric(age)) |>
  summarise(Mean = mean(age, na.rm = TRUE),
            SD = sd(age, na.rm = TRUE)) |>
  mutate_all(.funs = janitor::round_half_up, digits = 1) |>
  kable() |>
  add_header_above(header = c("Age" = 2)) |>
  kable_classic(full_width = FALSE)

```

## Gender

```{r}

data_processed_after_exclusions |> 
  rename(Gender = gender) |>
  group_by(Gender) |> 
  summarise(n = n()) |> 
  mutate(Percent = paste0(round_half_up((n / sum(n)) * 100, 1), "%")) |>
  mutate(Gender = stringr::str_to_sentence(Gender)) |> # Change the case of the Gender variable so that it prints nicely
  kable() |>
  kable_classic(full_width = FALSE)

```

# Descriptives

Descriptive statistics and plots of the measures (excluding the demographics variables)

## Self-reported evaluations


### Cronbachs Alpha
raw alpha = 0.876904!

```{r}

library(psych)

alpha_result<-alpha(subset(data_processed_after_exclusions, select = c("like", "prefer", "positive")))
                    #, check.keys = T) for inverted items
print(alpha_result)


```


### Descriptive stats

```{r}

# overall self-reported evaluations
dat_mean_ratings <- data_processed_after_exclusions |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# self-reported evaluations by gender category
dat_mean_ratings_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_mean_ratings,
          dat_mean_ratings_by_gender) |>
  select(Subset = group, Mean, SD, n) |> # select variables of interest, and rename one 
  mutate(Subset = stringr::str_to_sentence(Subset)) |> # Change the case of the Subset variable so that it prints nicely
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "Self-reported evaluations" = 3)) |>
  kable_classic(full_width = FALSE)

```

### Descriptive plot

```{r}

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation)) +
  geom_histogram(binwidth = 1,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("Mean self-reported evaluation") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(1, 7)) +
  theme(panel.grid.minor = element_blank())

```

## AMP evaluations

### Descriptive stats

\TODO add table of means, SDs, Ns

```{r}


# overall AMP scores
dat_AMP_means <- data_processed_after_exclusions |>
  summarise(Mean = mean(AMP_score, na.rm = TRUE),
            SD = sd(AMP_score, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# AMP Scores by gender category
dat_AMP_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(AMP_score, na.rm = TRUE),
            SD = sd(AMP_score, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_AMP_means,
          dat_AMP_by_gender) |>
  select(Subset = group, Mean, SD, n) |>
  mutate(Subset = stringr::str_to_sentence(Subset)) |>
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "AMP Scores" = 3)) |>
  kable_classic(full_width = FALSE)


```

### Descriptive plots

```{r}

ggplot(data_processed_after_exclusions, aes(x = AMP_score)) +
  geom_histogram(binwidth = 0.05,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("AMP score") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 10))

```

# Analyses & hypothesis tests

## Self-reported evaluations are correlated with evaluations on the AMP

### Plot

```{r}

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(y = AMP_score,
           x = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  ylab("AMP score") +
  xlab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

```

More complex plots:

#### Axial hisograms

Scatter plots with axial histograms using ggExtra: https://cran.r-project.org/web/packages/ggExtra/vignettes/ggExtra.html



\TODO add axial histograms to a scatter plot. In a single plot, present different regression lines split by gender, and separate axial histograms for each gender.

```{r}
#install.packages("ggExtra")

#scatter Plots, with regression lines, without histograms - each single plot 
ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, colour = gender)) +
  geom_point() +
  scale_colour_manual(values = c("female"="#996699","male" = "#777777","nonbinary" =  "#e89d97"))+
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(gender ~ ., scales = "free_y", space = "free_y")  #makes multiple plots

#scatter Plots, with regression lines, without histograms - one plot 
fr_MARG<- ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, colour = gender)) +
  geom_point() +
  scale_colour_manual(values = c("female"="#996699","male" = "#777777","nonbinary" =  "#e89d97"))+
  geom_smooth(method = "lm", se = FALSE)
print(fr_MARG)



ggMarginal(fr_MARG,type = "histogram", groupColour = TRUE, groupFill = TRUE)


```


#### Labelled points

Label points using ggrepel: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html

\TODO Label the points in a scatter plot using their participant codes.

```{r}

#install.packages("ggrepel")
library(ggrepel)

#labelled with participant codes
ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, label = subject, colour = gender)) +
  geom_point() +
  geom_text_repel(data = subset(data_processed_after_exclusions, subject %in% c("216287717", "247697997", "881713870")), aes(label = subject), color = "black", box.padding = 0.5) +
  scale_colour_manual(values = c("female" = "#996699", "male" = "#777777", "nonbinary" =  "#e89d97")) +
  labs(title = "labelled subjects 216287717, 881713870 and 247697997")



#labelled one group
ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, label = subject, colour = gender)) +
  geom_point() +
  geom_text_repel(data = subset(data_processed_after_exclusions, gender == "nonbinary"), aes(label = subject), color = "black", box.padding = 0.5) +
  scale_colour_manual(values = c("female" = "#996699", "male" = "#777777", "nonbinary" =  "#e89d97")) +
  labs(title = "Just the nonbinary are labelled")



#SINGLE PLOTS WITH LABELS!!!
#PREPARE DATASETS
data_p_a_e_nb <- data_processed_after_exclusions |>
  filter(gender == "nonbinary")

data_p_a_e_female <-data_processed_after_exclusions |>
  filter(gender == "female")

data_p_a_e_male <- data_processed_after_exclusions |>
  filter(gender == "male")


#for the Saving and COmbine Task

#NONBINÄRY
p_label <- ggplot(data_p_a_e_nb, aes(AMP_score, mean_evaluation, label = subject)) +
  geom_point(color = "#e89d97")

p_label + geom_text_repel() + labs(title = "plot of nonbinarys")


#FEMALE - to many overlaps
p_f_label <- ggplot(data_p_a_e_female, aes(AMP_score, mean_evaluation, label = subject)) +
  geom_point(color = "#7a060a")

p_f_label + geom_text_repel() + labs(title = "plot of females")

#MALE - to many overlaps
p_m_label <- ggplot(data_p_a_e_male, aes(AMP_score, mean_evaluation, label = subject)) +
  geom_point(color = "#777777")

p_m_label + geom_text_repel() + labs(title = "plot of males")

#ALL 

p_all_label <-ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, label = subject, colour = gender)) +
  geom_point() +
  scale_colour_manual(values = c("female" = "#7a060a", "male" = "#777777", "nonbinary" =  "#e89d97")) +
  labs(title = "For the other Tasks")

p_all_label +geom_text_repel(color = "black") + labs(title = "plot of all genders")




```

#### Magnify areas

Magnify areas of your plot with ggmagnify: https://hughjonesd.github.io/ggmagnify/

\TODO Magnify an area of one of your scatter plots, eg where there are a lot of data points in a small area.

```{r}
#install.packages("ggmagnify", repos = c("https://hughjonesd.r-universe.dev", 
#                 "https://cloud.r-project.org"))

#FEMALE - to many overlaps

from <- c(xmin =0.8,xmax = 1, ymin = 0.8, ymax = 1.2)
# Names xmin, xmax, ymin, ymax are optional:
to <- c(0.25,0.75, 2,3)

p_f_label + geom_magnify(from = from, to = to)+
    labs(title = "Magnify some female participants")

#or 

p_m_label + geom_magnify(from = c(0.46, 0.65, 0.8,  1.2), to = c(0.3,0.8, 3,4))+
   labs(title = "Magnify some male participants")

#nonbinary to magnify would be a bit sad, because they are just three people



```

### Test
\TODO run an appropriate test. Below the output, interpret the results. Consider using `easystats::report()`, but you can do this manually if you prefer.
```{r}

#remotes::install_github("easystats/report") <- something did go wrong


#The Pearson's product-moment correlation shows a negative correlation between AMP Score and Mean evaluation (r = -0.12, 95% CI [-0.32, 0.09]), but this is not statistically significant due to the relatively high p-value (t(88) = -1.17, p = 0.244), Accordingly, I would assume that there is no correlation between mean evaluation and the AMP score. 



#I did a Correlation between mean_evaluation and AMP_score
Correlation <- cor(data_processed_after_exclusions$mean_evaluation, data_processed_after_exclusions$AMP_score)|>
  print()

#some additional tests
correlation_test <- cor.test(data_processed_after_exclusions$mean_evaluation, data_processed_after_exclusions$AMP_score)|>
  print()


#easystats::report() <- somehow this does not work, so I tried other stuff out

report_table(correlation_test)
report_effectsize(correlation_test)





#for fun and to try out
report_table(data_processed_after_exclusions$mean_evaluation)
report_table(data_processed_after_exclusions$AMP_score)

report_statistics(correlation_test, table = NULL)
report_parameters(correlation_test)

#


```


\TODO 

## Self-reported evalautions differ between men and women
```{r}



# Prepare the data
data_p_e_without_nb <- data_processed_after_exclusions %>%
    filter(gender %in% c("female", "male"))


#t test
t_test_result <- t.test(mean_evaluation ~ gender, data = data_p_e_without_nb)
print(t_test_result)

#for interpreatation and report see below -> #Test

```
### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

```{r}

#Split Histogram
ggplot(data_processed_after_exclusions, 
       aes(x = mean_evaluation, group= gender, fill = gender)) +
  facet_grid(~gender)+
  geom_histogram(binwidth = 1) +
  labs(title = "Self-reported Evaluations by Gender",
       x = "Mean evaluation",
       y = "Frequency") +
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"))


#Split Violin
ggplot(data_processed_after_exclusions, 
       aes(y = mean_evaluation, x = gender, fill =gender)) +
  geom_violin(show.legend = FALSE) +
  labs(title = "Self-reported Evaluations by Gender",
       y = "Mean evaluation",
       x = "Gender")+
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"))


#raincloud plot
  ggplot(data_processed_after_exclusions, aes(y = gender, x = mean_evaluation, fill = gender)) +
  geom_density_ridges(alpha = 0.7, scale = 0.5) +
  geom_point(position = position_jitter(), alpha = 0.7, aes(color = gender)) +
  scale_fill_manual(values = c("female" = "#996699", "male" = "#777777", "nonbinary" = "#e89d97")) +
  scale_color_manual(values = c("female" = "#4d334d", "male" = "#333333", "nonbinary" = "#8c4d42"))
  #von unten nach oben!

  
    ggplot(data_processed_after_exclusions, aes(y = gender, x = mean_evaluation, fill = gender)) +
  geom_density_ridges(alpha = 0.7, scale = 0.5, position = position_nudge(x = 0.3, y = 0.0)) +
   geom_point(position = position_jitter(), alpha = 0.7, aes(color = gender)) +
  scale_fill_manual(values = c("female" = "#996699", "male" = "#777777", "nonbinary" = "#e89d97")) +
  scale_color_manual(values = c("female" = "#4d334d", "male" = "#333333", "nonbinary" = "#8c4d42"))



    
```

### Test

\TODO run an appropriate test. Below the output, interpret the results: write a few sentences that report and interpret the results following APA reporting style.



```{r}
#A Welch Two Sample t-test was conducted to examine the mean evaluation between men and women. The women achieved a mean of 1.32 and the men a mean of 1.81. The mean difference is estimated to be -0.49 (95% CI [-0.86, -0.12]), indicating that, on average, male participants scored higher than the female participants. The t-statistic is indicative of a significant difference (t(83.14) = -2.62, p = 0.011). The effect size, measured by Cohen's d, is medium (-0.57, 95% CI [-1.01, -0.13]).
#These results show that there is a significant difference between men and women in terms of their mean evaluation scores, men gave higher scores on the scales than women.


report_table(t_test_result)
report_effectsize(t_test_result)


# T TEST
```

## Evaluations on the Affect Misattribution Procedure differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

This time, vary the labeling and order of the legend, e.g., capitalise "Men" and "Women", and know how to change the order of the factors.

```{r}
#REARRANGE the order of the factors <- one way
data_p_a_e_rearranged <- data_processed_after_exclusions |> 
  mutate(gender = factor(gender, levels = c("nonbinary", "female", "male")))
#other way with aes(y = , x = factor(VARIABLE, levels = c("order")...is soetimes more complicated


#Split Histogram
ggplot(data_p_a_e_rearranged, 
       aes(x = AMP_score, group= gender, fill = gender)) +
   facet_grid(~gender, labeller = labeller(gender = c("nonbinary" = "Nonbinary", "female" = "Women", "male" = "Men"))) +
  geom_histogram(binwidth = 1) +
  labs(title = "AMP scores by Gender",
       x = "AMP Scores",
       y = "Frequency",
       fill = "Gender") +
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"),
                    breaks = c("nonbinary", "female",  "male"),
                    labels=c("Nonbinary", "Women", "Men"))



#Split Violin rearrange in aes()
ggplot(data_p_a_e_rearranged, 
       aes(y = AMP_score, x = factor(gender, levels = c("female", "male", "nonbinary")), 
           fill = gender)) +
  geom_violin(show.legend = FALSE) +
  labs(title = "AMP Scores by Gender",
       y = "AMP Scores",
       x = "Gender",
       fill = "Gender") +
  scale_fill_manual(values = c("female" = "#996699", "male" = "#777777", "nonbinary" = "#e89d97"),
                    breaks = c("female", "male", "nonbinary")) +
  scale_x_discrete(labels = c("Female", "Male", "Nonbinary"))



#raincloud plot

ggplot(data_p_a_e_rearranged, 
       aes(y = gender, x = AMP_score, fill = gender)) +
  geom_density_ridges(alpha = 0.7, scale = 0.5) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.2, jitter.width = 0.5),
              alpha = 0.5, aes(color = gender), show.legend = TRUE) +
  labs(title = "AMP scores by Gender",
       x = "AMP Scores",
       y = "Gender",
       fill ="Gender",
       color = "Gender") +
  scale_fill_manual(values = c("female" = "#996699", "male" = "#777777", "nonbinary" = "#e89d97"),
                    breaks = c("male", "female", "nonbinary"),  
                    labels = c("Male", "Female", "Nonbinary")) +
  scale_color_manual(values = c("female" = "#4d334d", "male" = "#333333", "nonbinary" = "#8c4d42"),
                     breaks = c("male", "female", "nonbinary"),
                     labels = c("Male", "Female", "Nonbinary")) +
  scale_y_discrete(labels = c("Nonbinary", "Female", "Male"))


?position_jitterdodge

```

### Test

\TODO run an appropriate test. Below the output, print an interpretation of the results generated by the 'easystats' package [report](https://easystats.github.io/report/). I.e., use `report::report()`.

```{r}


#t test
AMP_t_test_result <- t.test(AMP_score ~ gender, data = data_p_e_without_nb)
print(AMP_t_test_result)


report_table(AMP_t_test_result)
report_effectsize(AMP_t_test_result)

#Interpretation
report_text(AMP_t_test_result)

#The Welch Two Sample t-test testing the difference of AMP_score by gender (mean in group female =
#0.58, mean in group male = 0.58) suggests that the effect is positive, statistically not
#significant, and very small (difference = 3.16e-03, 95% CI [-0.08, 0.09], t(76.08) = 0.07, p =
#0.942; Cohen's d = 0.02, 95% CI [-0.43, 0.47])



```


## Combining plots

Combine plots using patchwork: https://patchwork.data-imaginist.com/

\TODO Combine at least three of the above plots into one.

```{r}
#install.packages('patchwork')

#one varaiant
p_f_label + p_m_label + p_label

#other variant
(p_f_label + p_m_label + p_label)/
  p_all_label

```

## Saving plots

Save plots to disk with `ggsave()`

\TODO Save the above combined plot to disk as both .png and .pdf. Ensure the png has at least 300dpi resolution.

```{r}

to_save<-(p_f_label + p_m_label + p_label)/
  p_all_label



dir.create("../data/plots/")

ggsave("../data/plots/Gender_Comb_plot.png", plot = to_save, dpi = 300, device = "png")

ggsave("../data/plots/Gender_Comb_plot.pdf", plot = to_save, device = "pdf")


```

# Session info

```{r}

sessionInfo()
#for reprocthings

```



