---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Analysis"
author: "Template: Ian Hussey; content: Tina Puskaric"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

# set knit options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Dependencies

```{r}


library(tidyverse)
library(knitr)
library(kableExtra)
library(janitor)
library(scales)
# install.packages("ggmagnify", repos = c("https://hughjonesd.r-universe.dev",
#                 "https://cloud.r-project.org"))
library(ggmagnify)
library("ggExtra")
library("ggplot2")
library("viridis") 
library("ggsci")
library(ggrepel)
library(ggridges)
library(patchwork)
library(easystats)
library(psych)



```
#SET.SEED

```{r}
set.seed(333) 

```

# Data

- Load the processed data and apply the global exclusions.

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv")

data_processed_after_exclusions <- data_processed |>
  filter(exclude_participant == "include")

```

# Sample descriptives

## Sample size before exclusions

```{r}

data_processed |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("Whole sample" = 1)) |>
  kable_classic(full_width = FALSE)

```

## Sample size after exclusions

Sample used in subsequent analyses

```{r}

data_processed_after_exclusions |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("For analysis" = 1)) |>
  kable_classic(full_width = FALSE)

```

## Age

```{r}

data_processed_after_exclusions |>
  mutate(age = as.numeric(age)) |>
  summarise(Mean = mean(age, na.rm = TRUE),
            SD = sd(age, na.rm = TRUE)) |>
  mutate_all(.funs = janitor::round_half_up, digits = 1) |>
  kable() |>
  add_header_above(header = c("Age" = 2)) |>
  kable_classic(full_width = FALSE)

```

## Gender

```{r}

data_processed_after_exclusions |> 
  rename(Gender = gender) |>
  group_by(Gender) |> 
  summarise(n = n()) |> 
  mutate(Percent = paste0(round_half_up((n / sum(n)) * 100, 1), "%")) |>
  mutate(Gender = stringr::str_to_sentence(Gender)) |> 
  kable() |>
  kable_classic(full_width = FALSE)

```

# Descriptives

Descriptive statistics and plots of the measures (excluding the demographics variables)

## Self-reported evaluations


### Cronbachs Alpha
raw alpha = 0.876904!

```{r}

library(psych)

alpha_result<-alpha(subset(data_processed_after_exclusions, select = c("like", "prefer", "positive")))
                    #, check.keys = T) for inverted items
print(alpha_result)


```


### Descriptive stats

```{r}

# overall self-reported evaluations
dat_mean_ratings <- data_processed_after_exclusions |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# self-reported evaluations by gender category
dat_mean_ratings_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_mean_ratings,
          dat_mean_ratings_by_gender) |>
  select(Subset = group, Mean, SD, n) |> 
  mutate(Subset = stringr::str_to_sentence(Subset)) |>
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "Self-reported evaluations" = 3)) |>
  kable_classic(full_width = FALSE)

```

### Descriptive plot

```{r}

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation)) +
  geom_histogram(binwidth = 0.5,
                 boundary = 1,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = "black") + 
  labs(x = "Mean Self-Reported Evaluation",
       y ="Frequency",
       title = "Distribution of Self-Reported Evaluation ") +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(1, 7)) +
  theme(panel.grid.minor = element_blank()) +
  theme_minimal()

```

## AMP evaluations

### Descriptive stats
- add table of means, SDs, Ns

```{r}


# overall AMP scores
dat_AMP_means <- data_processed_after_exclusions |>
  summarise(Mean = mean(AMP_score, na.rm = TRUE),
            SD = sd(AMP_score, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# AMP Scores by gender category
dat_AMP_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(AMP_score, na.rm = TRUE),
            SD = sd(AMP_score, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_AMP_means,
          dat_AMP_by_gender) |>
  select(Subset = group, Mean, SD, n) |>
  mutate(Subset = stringr::str_to_sentence(Subset)) |>
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "AMP Scores" = 3)) |>
  kable_classic(full_width = FALSE)


```

### Descriptive plots

```{r}
#used a diffrent colour palette

ggplot(data_processed_after_exclusions, aes(x = AMP_score)) +
  geom_histogram(binwidth = 0.05,
                 boundary = 0,
                 fill = brewer_pal(palette = "Spectral")(1),
                 color = "black") + 
  labs(x = "AMP Score",
       y = "Frequency",
       title = "Distribution of AMP Score") +
  scale_x_continuous(breaks = pretty_breaks(n = 10)) +
  theme_minimal()


```

# Analyses & hypothesis tests

## Self-reported evaluations are correlated with evaluations on the AMP

### Plot

```{r}

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = brewer_pal(palette = "Set1")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = "darkred") +
  labs(x = "AMP Score",
       y = "Mean Self-Reported Evaluation",
       title = "Correlation between AMP Score and Self_reports") +
  scale_y_continuous(limits = c(0.5, 7.2), breaks = c(1: 7)) +
  scale_x_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
  theme_minimal() 

#without the regression line
ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = brewer_pal(palette = "Set1")(1),
              alpha = 0.5) +
   labs(x = "AMP Score",
       y = "Mean Self-Reported Evaluation",
       title = "Correlation between AMP Score and Self_reports") +
  scale_y_continuous(limits = c(0.5, 7.2), breaks = c(1: 7)) +
  scale_x_continuous(limits = c(-0.1, 1)) +
  theme_minimal() 



#actually the same, but switched the X and Y Scale
ggplot(data_processed_after_exclusions, 
       aes(y = AMP_score,
           x = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.25, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.25, option = "mako")(1)) +
  labs(y = "AMP Score",
       x = "Mean Self-Reported Evaluation",
       title = "Correlation between AMP Score and Self_reports") +
  scale_x_continuous(limits = c(0.5, 7), breaks = c(1: 7)) +
  scale_y_continuous(limits = c(-0.1, 1)) +
  theme_minimal() 



```

More complex plots:

#### Axial hisograms

Scatter plots with axial histograms using ggExtra: https://cran.r-project.org/web/packages/ggExtra/vignettes/ggExtra.html

- add axial histograms to a scatter plot. In a single plot, present different regression lines split by gender, and separate axial histograms for each gender.

```{r}

#scatter Plots, with regression lines, without histograms - each single plot 
ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, colour = gender)) +
  geom_point() +
  scale_colour_manual(values = c("female"="#996699","male" = "#777777","nonbinary" =  "#e89d97"),
                      name = "Gender",
                      labels = c("Female", "Male", "Nonbinary"))+
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(gender ~ ., scales = "free_y", space = "free_y")+  #makes multiple plots
  labs(y = "Mean Evaluation",
       x = "AMP Score",
       title = "Scatterplot with Regressions") +
  scale_y_continuous(limits = c(0.5, 7), breaks = c(1: 7)) +
  theme_gray()

#scatter Plots, with regression lines, without histograms - one plot 
fr_MARG<- ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, colour = gender)) +
  geom_point() +
 scale_colour_manual(values = c("female"="#996699","male" = "#777777","nonbinary" =  "#e89d97"),
                      name = "Gender",
                      labels = c("Female", "Male", "Nonbinary"))+
  geom_smooth(method = "lm", se = FALSE) +
  labs(y = "Mean Evaluation",
       x = "AMP Score",
       title = "Scatterplot with Regressions")+
  scale_y_continuous(limits = c(0.5, 7), breaks = c(1: 7)) +
   theme_gray() +
  theme(legend.position = "left")
print(fr_MARG)


#with histogramms above
#thats why the legend is on the left side
#it would look ugly if on the right side with the histogramms
#Somehow in the html version it looks really weird
#but in R it looks fine... so don't know
ggMarginal(fr_MARG, type = "histogram", groupColour = TRUE, groupFill = TRUE)



```


#### Labelled points

Label points using ggrepel: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html

- Label the points in a scatter plot using their participant codes.

```{r}

#labelled with participant codes - 3 each one of a group
ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, label = subject, colour = gender)) +
  geom_point() +
  geom_text_repel(data = subset(data_processed_after_exclusions, subject %in% c("216287717", "247697997", "881713870")),
                  aes(label = subject), color = "black", box.padding = 0.5) +
  scale_colour_manual(values = c("female"="#996699","male" = "#777777","nonbinary" =  "#e89d97"),
                      name = "Gender",
                      labels = c("Female", "Male", "Nonbinary")) +
  scale_y_continuous(limits = c(0.5, 7), breaks = c(1: 7)) +
  labs(title = "Labelled Subjects 216287717, 881713870 and 247697997",
       y = "Mean Evaluation",
       x = "AMP Score")



#labelled one group - nonbinary
ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, label = subject, colour = gender)) +
  geom_point() +
  geom_text_repel(data = subset(data_processed_after_exclusions, gender == "nonbinary"), aes(label = subject), color = "black", box.padding = 0.5) +
  scale_colour_manual(values = c("female"="#996699","male" = "#777777","nonbinary" =  "#e89d97"),
                      name = "Gender",
                      labels = c("Female", "Male", "Nonbinary")) +
  scale_y_continuous(limits = c(0.5, 7), breaks = c(1: 7)) +
  labs(title = "Just the Nonbinary are Labelled",
       y = "Mean Evaluation",
       x = "AMP Score")

```

Single Plots

```{r}
#SINGLE PLOTS WITH LABELS!!!
#PREPARE DATASETS
data_p_a_e_nb <- data_processed_after_exclusions |>
  filter(gender == "nonbinary")

data_p_a_e_female <-data_processed_after_exclusions |>
  filter(gender == "female")

data_p_a_e_male <- data_processed_after_exclusions |>
  filter(gender == "male")


#for the Saving and Combine Task

#NONBINÄRY
p_label <- ggplot(data_p_a_e_nb, aes(AMP_score, mean_evaluation, label = subject)) +
  geom_point(color = "#e89d97")+
  scale_y_continuous(limits = c(0.5, 7), breaks = c(1: 7)) +
  labs(y = "Mean Evaluation",
       x = "AMP Score") +
  labs(title = "Plot of Nonbinarys") +
  theme_gray()

p_label + geom_text_repel() 


#FEMALE - to many overlaps
p_f_label <- ggplot(data_p_a_e_female, aes(AMP_score, mean_evaluation, label = subject)) +
  geom_point(color = "#7a060a")+
  scale_y_continuous(limits = c(0.5, 7), breaks = c(1: 7)) +
  labs(y = "Mean Evaluation",
       x = "AMP Score") +
  labs(title = "Plot of Females") +
  theme_gray()

p_f_label + geom_text_repel() 


#MALE - to many overlaps
p_m_label <- ggplot(data_p_a_e_male, aes(AMP_score, mean_evaluation, label = subject)) +
  geom_point(color = "#777777")+
  scale_y_continuous(limits = c(0.5, 7), breaks = c(1: 7)) +
  labs(y = "Mean Evaluation",
       x = "AMP Score") +
  labs(title = "Plot of Males") +
  theme_gray()

p_m_label + geom_text_repel() 



#ALL 

p_all_label <-ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, label = subject, colour = gender)) +
  geom_point() +
   scale_colour_manual(values = c("female"="#996699","male" = "#777777","nonbinary" =  "#e89d97"),
                      name = "Gender",
                      labels = c("Female", "Male", "Nonbinary")) +
  scale_y_continuous(limits = c(0.5, 7), breaks = c(1: 7)) +
  labs(title = "Plot of all Genders",
      y = "Mean Evaluation",
       x = "AMP Score") +
  theme_gray()

p_all_label +geom_text_repel(color = "black")




```

#### Magnify areas

Magnify areas of your plot with ggmagnify: https://hughjonesd.github.io/ggmagnify/

- Magnify an area of one of your scatter plots, eg where there are a lot of data points in a small area.

```{r}


#FEMALE - to many overlaps

from <- c(xmin =0.8,xmax = 1, ymin = 0.8, ymax = 1.2)
# Names xmin, xmax, ymin, ymax are optional:
to <- c(0.25,0.75, 2,3)

p_f_label + geom_magnify(from = from, to = to)+
    labs(title = "Magnify some Female Participants")

#or 

p_m_label + geom_magnify(from = c(0.46, 0.65, 0.8,  1.2), to = c(0.3,0.8, 3,4))+
   labs(title = "Magnify some Male Participants")

#nonbinary to magnify would be a bit sad, because they are just three people



```

### Test
- run an appropriate test. Below the output, interpret the results. Consider using `easystats::report()`, but you can do this manually if you prefer.
```{r}

#remotes::install_github("easystats/report") <- something did go wrong


#The Pearson's product-moment correlation shows a negative correlation between AMP Score and Mean evaluation (r = -0.12, 95% CI [-0.32, 0.09]), but this is not statistically significant due to the relatively high p-value (t(88) = -1.17, p = 0.244), Accordingly, I would assume that there is no correlation between mean evaluation and the AMP score. 



#I did a Correlation between mean_evaluation and AMP_score
Correlation <- cor(data_processed_after_exclusions$mean_evaluation, data_processed_after_exclusions$AMP_score)|>
  print()

#some additional tests
correlation_test <- cor.test(data_processed_after_exclusions$mean_evaluation, data_processed_after_exclusions$AMP_score)|>
  print()


#easystats::report() <- somehow this does not work, so I tried other stuff out

report_table(correlation_test)
report_effectsize(correlation_test)





#for fun and to try out
report_table(data_processed_after_exclusions$mean_evaluation)
report_table(data_processed_after_exclusions$AMP_score)

report_statistics(correlation_test, table = NULL)
report_parameters(correlation_test)

#


```


## Self-reported evalautions differ between men and women
```{r}



# Prepare the data
data_p_e_without_nb <- data_processed_after_exclusions %>%
    filter(gender %in% c("female", "male"))


#t test
t_test_result <- t.test(mean_evaluation ~ gender, data = data_p_e_without_nb)
print(t_test_result)

#for interpreatation and report see below -> #Test

```
### Plot
- split histogram, split violin plot, raincloud plot, etc.

```{r}

#Split Histogram
ggplot(data_processed_after_exclusions, 
       aes(x = mean_evaluation, group= gender, fill = gender)) +
  facet_grid(~gender)+
  geom_histogram(binwidth = 1) +
  scale_x_continuous(limits = c(0.5, 7.1), breaks = c(1,3,5,7)) +
  labs(title = "Self-reported Evaluations by Gender",
       x = "Mean Evaluation",
       y = "Frequency") +
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"),
                    name = "Gender",
                    labels = c("female", "male", "nonbinary"))+
    theme_gray()


#Split Violin
ggplot(data_processed_after_exclusions, 
       aes(y = mean_evaluation, x = gender, fill =gender)) +
  geom_violin(show.legend = FALSE) +
  labs(title = "Self-reported Evaluations by Gender",
       y = "Mean evaluation",
       x = "Gender")+
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"))+
  scale_x_discrete(labels = c("female" = "Female", "male" = "Male", "nonbinary" = "Nonbinary"))+
    theme_gray()


#raincloud plot
  ggplot(data_processed_after_exclusions, aes(y = gender, x = mean_evaluation, fill = gender)) +
  geom_density_ridges(alpha = 0.7, scale = 0.5) +
  geom_point(position = position_jitter(), alpha = 0.7, aes(color = gender)) +
  scale_fill_manual(values = c("female" = "#996699", "male" = "#777777", "nonbinary" = "#e89d97"),
                    name = "Gender",
                    labels = c("Female", "Male", "Nonbinary")) +
  scale_color_manual(values = c("female" = "#4d334d", "male" = "#333333", "nonbinary" = "#8c4d42"),
                     name = "Gender",
                    labels = c("Female", "Male", "Nonbinary")) +
  scale_y_discrete(labels = c("female" = "Female", "male" = "Male", "nonbinary" = "Nonbinary"))+
  labs(title = "Rainclouds",
       x = "Mean evaluation",
       y = "Gender") +
  scale_x_continuous(limits = c(-1, 7.1), breaks = c(1,3,5,7)) +
    theme_gray()
#von unten nach oben!

    
```

### Test

- run an appropriate test. Below the output, interpret the results: write a few sentences that report and interpret the results following APA reporting style.



```{r}
#A Welch Two Sample t-test was conducted to examine the mean evaluation between men and women. The women achieved a mean of 1.32 and the men a mean of 1.81. The mean difference is estimated to be -0.49 (95% CI [-0.86, -0.12]), indicating that, on average, male participants scored higher than the female participants. The t-statistic is indicative of a significant difference (t(83.14) = -2.62, p = 0.011). The effect size, measured by Cohen's d, is medium (-0.57, 95% CI [-1.01, -0.13]).
#These results show that there is a significant difference between men and women in terms of their mean evaluation scores, men gave higher scores on the scales than women.


report_table(t_test_result)
report_effectsize(t_test_result)


# T TEST
```

## Evaluations on the Affect Misattribution Procedure differ between men and women

### Plot

- split histogram, split violin plot, raincloud plot, etc.

- This time, vary the labeling and order of the legend, e.g., capitalise "Men" and "Women", and know how to change the order of the factors.

I made some Titles Bold
```{r}
#REARRANGE the order of the factors <- one way
data_p_a_e_rearranged <- data_processed_after_exclusions |> 
  mutate(gender = factor(gender, levels = c("nonbinary", "female", "male")))
#other way with aes(y = , x = factor(VARIABLE, levels = c("order")...is soetimes more complicated


#Split Histogram
ggplot(data_p_a_e_rearranged, 
       aes(x = AMP_score, group= gender, fill = gender)) +
   facet_grid(~gender, labeller = labeller(gender = c("nonbinary" = "Nonbinary", "female" = "Women", "male" = "Men"))) +
  geom_histogram(binwidth = 1) +
  labs(title = "AMP scores by Gender",
       x = "AMP Scores",
       y = "Frequency",
       fill = "Gender") +
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"),
                    breaks = c("nonbinary", "female",  "male"),
                    labels=c("Nonbinary", "Women", "Men")) +
  theme(axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face = "bold"),
        legend.title = element_text(face = "plain"),
        plot.title = element_text(face = "bold"))



#Split Violin rearrange in aes()
ggplot(data_p_a_e_rearranged, 
       aes(y = AMP_score, x = factor(gender, levels = c("female", "male", "nonbinary")), 
           fill = gender)) +
  geom_violin(show.legend = FALSE) +
  labs(title = "AMP Scores by Gender",
       y = "AMP Scores",
       x = "Gender",
       fill = "Gender") +
  scale_fill_manual(values = c("female" = "#996699", "male" = "#777777", "nonbinary" = "#e89d97"),
                    breaks = c("female", "male", "nonbinary")) +
  scale_x_discrete(labels = c("Female", "Male", "Nonbinary"))+
  theme(axis.title.x = element_text(face = "plain"),
        axis.title.y = element_text(face = "plain"),
        plot.title = element_text(face = "bold"))



#raincloud plot
ggplot(data_p_a_e_rearranged, 
       aes(y = gender, x = AMP_score, fill = gender)) +
  geom_density_ridges(alpha = 0.7, scale = 0.5) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.2, jitter.width = 0.5),
              alpha = 0.5, aes(color = gender), show.legend = TRUE) +
  labs(title = "AMP scores by Gender",
       x = "AMP Scores",
       y = "Gender",
       fill ="Gender",
       color = "Gender") +
  scale_fill_manual(values = c("female" = "#996699", "male" = "#777777", "nonbinary" = "#e89d97"),
                    breaks = c("male", "female", "nonbinary"),  
                    labels = c("Male", "Female", "Nonbinary")) +
  scale_color_manual(values = c("female" = "#4d334d", "male" = "#333333", "nonbinary" = "#8c4d42"),
                     breaks = c("male", "female", "nonbinary"),
                     labels = c("Male", "Female", "Nonbinary")) +
  scale_y_discrete(labels = c("Nonbinary", "Female", "Male")) +
  scale_x_continuous(limits = c(-0.1, 1.1)) +
  theme_gray()+
  theme(axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face = "bold"),
        legend.title = element_text(face = "bold"),
        plot.title = element_text(face = "bold"))


```

### Test

- run an appropriate test. Below the output, print an interpretation of the results generated by the 'easystats' package [report](https://easystats.github.io/report/). I.e., use `report::report()`.

```{r}


#t test
AMP_t_test_result <- t.test(AMP_score ~ gender, data = data_p_e_without_nb)
print(AMP_t_test_result)


report_table(AMP_t_test_result)
report_effectsize(AMP_t_test_result)

#Interpretation
report_text(AMP_t_test_result)

#The Welch Two Sample t-test testing the difference of AMP_score by gender (mean in group female =
#0.58, mean in group male = 0.58) suggests that the effect is positive, statistically not
#significant, and very small (difference = 3.16e-03, 95% CI [-0.08, 0.09], t(76.08) = 0.07, p =
#0.942; Cohen's d = 0.02, 95% CI [-0.43, 0.47])



```


## Combining plots

Combine plots using patchwork: https://patchwork.data-imaginist.com/

\TODO Combine at least three of the above plots into one.

```{r}
#install.packages('patchwork')

#one varaiant
p_f_label + p_m_label + p_label

#other variant
(p_f_label + p_m_label + p_label)/
  p_all_label

```

## Saving plots

Save plots to disk with `ggsave()`

- Save the above combined plot to disk as both .png and .pdf. Ensure the png has at least 300dpi resolution.

```{r}

to_save <- (p_f_label + p_m_label + p_label)/
  p_all_label



dir.create("../data/plots/")

ggsave("../data/plots/Gender_Comb_plot.png", plot = to_save, dpi = 300, device = "png")

ggsave("../data/plots/Gender_Comb_plot.pdf", plot = to_save, device = "pdf")


```

# Session info

```{r}

sessionInfo()
#for reprocthings

```



