---
title: "Examining the relationship between the big-5 personality facets and implicit racial attitudes"
subtitle: "Data processing"
author: "Tina Puskaric"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(janitor)
library(stringr)
# library(readr)
# library(dplyr)
# library(tidyr)
# library(knitr)
# library(kableExtra)
# library(stringr)
# library(openxlsx)


```

# Get data

```{r}


#data_raw_demographics
data_raw_demographics <- read_csv("../data/raw/data_raw_demographics.csv") |>
  janitor::clean_names()


#data_raw_bfi
data_raw_bfi <- read_csv("../data/raw/data_raw_bfi.csv") |>
  janitor::clean_names()

#data_raw_iat
data_raw_iat <- read_csv("../data/raw/data_raw_iat.csv") |>
  janitor::clean_names()




```

# Demographics
- Extract age and gender from the raw demographics data.

```{r}
#zuerst in eine Wideform bringen - sex in gender und unique id in id umbenennen
data_age_gender <- data_raw_demographics|>
  select(id, variab
   pivot_wider(names_from = variable,
              values_from = response)|>
  rename(gender = sex, id = unique_id )


  mutate(gender = tolower(gender),
         gender = stringr::str_remove_all(gender, regex("\\W+")),
         gender == "f" ~ "female",
         gender == "m" ~ "male",
         TRUE ~ "other/missing/error",
         age = case_when(str_detect(age, "^[0-9]+$") ~ age, # if the value is only numbers -> keep it. 
                         TRUE ~ "other/missing/error")) 

unique(data_age_gender$age)
unique(data_age_gender$gender)
unique(data_age_gender$id)

#extrahiere
data_age <- data_age_gender |>
  select(id, age)

data_gender <- data_age_gender|>
  select(id, gender)|>
   mutate(gender = tolower(gender),
         gender = stringr::str_remove_all(gender, regex("\\W+")),
         gender == "f" ~ "female",
         gender == "m" ~ "male",
         TRUE ~ "other/missing/error")




```

# BFI Scale

## Scale adjusting + Sanity Check
-  Reverse score the negatively worded items: the extroversion scale items 2, 5 and 7, conscientiousness items 2, 4 5 and 9, neuroticism items 2, 5, and 7, agreeableness 1, 3, 6, and 8, and openness items 7 and 9.


```{r}


```
- Include a sanity check that assesses whether these list of item reversals, and your implementation of them, is likely to be correct: For each subscale, create a correlation table among the items (after reversals) and check that all correlations are positive. IN general, negative correlations among items are one indication that information about item reversals, or their implementation, is not correct. 
 
```{r}
#Sanity Check

```



## Data quality
- Check that the item level data does not violate the logical minimum and maximum scores (1 to 6). Create an exclusion variable and set participants with impossible data to "exclude".

- Check that all participants have complete data on the BFI scales they completed. Create an exclusion variable and set participants with incomplete data to "exclude".
```{r}


```


## Mean score
- Mean-score the subscales of the BFI scale. Each participant only got either 2 or 3 subscales. 

 - Check that the mean scores do not violate the min and max possible score (i.e., first determine this min and max score), and revise your scoring code if it does. 
```{r}


```

# IAT Scale

## D Score
- Score the trial-level IAT data using the Greenwald "D" score: Calculate a mean RT ("mean1") for blocks 3 and 6 (one score using trials from both blocks), a mean RT ("mean2") for blocks 4 and 7 (one score using trials from both blocks), and the SD of RTs in blocks 3, 4, 6 and 7 ("SD"). To calculate D: D = (mean2 - mean1)/SD. Blocks 1, 2, and 5 are practice blocks and must be discarded. 
```{r}


```


- Include a sanity check: check that all D scores are in the range -2 to +2. If not, revise your implementation of the scoring code. 

```{r}


```

## Exclusions
  - Create an exclusion variable and set participants with incomplete trial level IAT data to "exclude". Specifically, IAT should have 120 trials on the critical test blocks (i.e., blocks 3, 4, 6 and 7). Trials on the other (practice) blocks can be discarded.
  
```{r}


```

  - Create an exclusion variable for IAT performance: set participants with >10% of the participants trials are < 300ms, or if their accuracy is < than 75%. Only use trials from the critical test blocks when computing these (i.e., blocks 3, 4, 6 and 7).

```{r}


```

# Combine BFI & IAT
- Combine the demographics, BFI, and IAT data into one data frame. This data frame should be one-row-one-participant. Both the mean scored and item level BFI data should be present in the dataset.
```{r}



```

# Master exclusions
- Create a master exclude variable from the individual exclude variables. 
```{r}



```

# Write to disk
- Save the processed data to the data/processed/ folder as "data_processed.csv". 
```{r}

# exists already
#dir.create("../data/processed/")

# save data
#write_csv(data_processed, "../data/processed/data_processed.csv")

```

# Codebook 

- Create a codebook for the processed data file that explains what each variable represents.

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv")



if(!file.exists("../data/processed/data_processed_codebook.xlsx")){
  codebook_template <- data.frame(variable = colnames(data_processed)) |>
    mutate(explanation = NA)

  write.xlsx(codebook_template, file = "../data/processed/data_processed_codebook.xlsx")
}

```



# Session info

```{r}

sessionInfo()

```


