---
title: "Examining the relationship between the big-5 personality facets and implicit racial attitudes"
subtitle: "Data processing"
author: "Tina Puskaric"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(janitor)
library(stringr)
# library(readr)
library(dplyr)
# library(tidyr)
# library(knitr)
# library(kableExtra)
# library(stringr)
# library(openxlsx)


```

# Get data

```{r}


#data_raw_demographics
data_raw_demographics <- read_csv("../data/raw/data_raw_demographics.csv") |>
  janitor::clean_names()


#data_raw_bfi
data_raw_bfi <- read_csv("../data/raw/data_raw_bfi.csv") |>
  janitor::clean_names()

#data_raw_iat
data_raw_iat <- read_csv("../data/raw/data_raw_iat.csv") |>
  janitor::clean_names()




```

# Demographics
- Extract age and gender from the raw demographics data.

```{r}
#zuerst in eine Wideform bringen - sex in gender und unique id in id umbenennen
#muss jetzt schon NA in ID droppen, weil ich sonst die Daten nicht anschauen kann und R abstürzt
data_age_gender <- data_raw_demographics|>
  na.omit(data_raw_demographics$unique_id)|> 
  pivot_wider(names_from = variable,
              values_from = response)|>
  rename(gender = sex, ID = unique_id )
  

unique(data_age_gender$age)
unique(data_age_gender$gender) #wie sie die Geschlechtsangabe erfasst haben
unique(duplicated(data_age_gender$id)) #ob es Duplicate gibt - anscheinend nicht


data_age_gender <- data_age_gender |> 
  filter(!duplicated(ID))|>
  mutate(gender = stringr::str_remove_all(gender, regex("\\W+")), 
         gender = case_when(gender == "f" ~ "female",
                            gender == "m" ~ "male",
                            TRUE ~ "other/missing/error"),
         age = case_when(str_detect(age, "^[0-9]+$") ~ age, 
                         TRUE ~ "other/missing/error")) 

#extrahiere
data_age <- data_age_gender |>
  select(ID, age)

data_gender <- data_age_gender|>
  select(ID, gender)


```

# BFI Scale

## Scale adjusting 
-  Reverse score the negatively worded items: the 
extroversion scale items 2, 5 and 7,  
conscientiousness items 2, 4 5 and 9, 
neuroticism items 2, 5, and 7, 
agreeableness 1, 3, 6, and 8, and 
openness items 7 and 9.


```{r}

#geht nur bis 1-6, aber die 0, 7 und NA werden später behandelt
#habe Listen erzeugt, welche Items reversed werden müssen, um es übersichtlicher zu halten
r_agreeableness <- c("bfi_a1", "bfi_a3", "bfi_a6", "bfi_a8")
r_openness <- c("bfi_o7", "bfi_o9")
r_neuroticism <- c("bfi_n2", "bfi_n5", "bfi_n7")
r_conscientiousness <- c("bfi_c2", "bfi_c4","bfi_c5", "bfi_c9")
r_extroversion <- c("bfi_e2", "bfi_e5", "bfi_e7")

#reverse die Angaben mit case_when
data_raw_bfi_adjusted <- data_raw_bfi |>
  rename(ID = unique_id) |> 
  mutate_at(vars(r_agreeableness, r_openness, r_neuroticism, r_conscientiousness, r_extroversion), list(~ case_when(
    . == 6 ~ 1,
    . == 5 ~ 2,
    . == 4 ~ 3,
    . == 3 ~ 4,
    . == 2 ~ 5,
    . == 1 ~ 6)))


```

## Sanity Check
- Include a sanity check that assesses whether these list of item reversals, and your implementation of them, is likely to be correct: For each subscale, create a correlation table among the items (after reversals) and check that all correlations are positive. 
 
```{r}
#erzeuge die Subskalen und filtere die Antworten nach 1-6, somit werden die NA und 0 und 7 als Antworten ignoriert

#um die genauen namen zu sehen und wie viele Items jeweils nötig sind
colnames(data_raw_bfi_adjusted)


#Die Korrelationen sind alle positiv, scheint dass der Reverse funktioniert hat


# Agreeableness hat 9 items
agreeableness = c("bfi_a1", "bfi_a2", "bfi_a3", "bfi_a4", "bfi_a5", "bfi_a6", "bfi_a7", "bfi_a8", "bfi_a9")

data_bfi_agreeableness <- data_raw_bfi_adjusted |>
  select(agreeableness) |>
  filter_all(all_vars(. %in% 1:6)) |>
  na.omit()

cor_agreeableness <- cor(data_bfi_agreeableness)

#Testversuch wie es aussieht, wenn die Items nicht reversed sind!
# NOT_REVER_data_bfi_agreeableness <- data_raw_bfi |>
#   select(bfi_a1, bfi_a2, bfi_a3, bfi_a4, bfi_a5, bfi_a6, bfi_a7, bfi_a8, bfi_a9) |>
#   filter_all(all_vars(. %in% 1:6)) |>
#   na.omit()
# 
# NOT_REVER_cor_agreeableness <- cor(NOT_REVER_data_bfi_agreeableness)

# Conscientiousness hat 9 items
conscientiousness<- c("bfi_c1", "bfi_c2", "bfi_c3", "bfi_c4", "bfi_c5", "bfi_c6", "bfi_c7", "bfi_c8", "bfi_c9")

data_bfi_conscientiousness <- data_raw_bfi_adjusted |>
  select(conscientiousness) |>
  filter_all(all_vars(. %in% 1:6)) |>
  na.omit()

cor_conscientiousness <- cor(data_bfi_conscientiousness)


# Neuroticism hat 8 items
neuroticism <- c("bfi_n1", "bfi_n2", "bfi_n3", "bfi_n4", "bfi_n5", "bfi_n6", "bfi_n7", "bfi_n8")

data_bfi_neuroticism <- data_raw_bfi_adjusted |>
  select(neuroticism) |>
  filter_all(all_vars(. %in% 1:6)) |>
  na.omit()

cor_neuroticism <- cor(data_bfi_neuroticism)


# Openness hat 9 items
openness <- c("bfi_o1", "bfi_o2", "bfi_o3", "bfi_o4", "bfi_o5", "bfi_o6", "bfi_o7", "bfi_o8", "bfi_o9")

data_bfi_openness <- data_raw_bfi_adjusted |>
  select(openness) |>
  filter_all(all_vars(. %in% 1:6)) |>
  na.omit()

cor_openness <- cor(data_bfi_openness)


# Extroversion hat 8 items
extroversion <- c("bfi_e1", "bfi_e2", "bfi_e3", "bfi_e4", "bfi_e5", "bfi_e6", "bfi_e7", "bfi_e8")

data_bfi_extroversion <- data_raw_bfi_adjusted |>
  select(extroversion) |>
  filter_all(all_vars(. %in% 1:6)) |>
  na.omit()

cor_extroversion <- cor(data_bfi_extroversion)


```



## Data quality
- Check that the item level data does not violate the logical minimum and maximum scores (1 to 6). Create an exclusion variable and set participants with impossible data to "exclude".


- Check that all participants have complete data on the BFI scales they completed. Create an exclusion variable and set participants with incomplete data to "exclude".

```{r}

#habe zwei Datasätze gemacht und die Teilnerhmer aufgteilt in den Gruppen: A & o <- Teilnehmer die nur diese zwei Skalen ausgefüllt haben 
# N und E und C <- Teilnehmer, die nur diese drei Skalen ausgefüllt haben

#ich kann sie so gruppieren bezöglich der exclude_impossible <- weil in der Masterexklusion müsste ich die dann sowieso excluden
#zuerst unterteile ich den Datensatz nach ID und den gewünschten Items, falls die Teilnehmer gar keine Items aus der gewünschten Skalen gelöst haben, werde ich diese aus diesem Datensatz entfernen und sie dann im anderen Datensatz berücksichtigen, falls sie dort welche Items gelöst haben


#für Agree und Openess -> 2 scales
openness <- c("bfi_o1", "bfi_o2", "bfi_o3", "bfi_o4", "bfi_o5", "bfi_o6", "bfi_o7", "bfi_o8", "bfi_o9")
agreeableness = c("bfi_a1", "bfi_a2", "bfi_a3", "bfi_a4", "bfi_a5", "bfi_a6", "bfi_a7", "bfi_a8", "bfi_a9")

data_bfi_A_O <- data_raw_bfi_adjusted |>
  select(ID, agreeableness, openness) |>
  rowwise()|> #wenn rowwise fehlt, wird der Code nicht funktionieren 
  filter(!if_all(-ID, is.na)) |>
  mutate(exclude_impossible = if_else(all(c_across(c(agreeableness, openness)) %in% 1:6), "include", "exclude"))|>
  mutate(exclude_not_completed = if_else(any(is.na(c_across(c(agreeableness, openness)))), "exclude", "include"))



#für Extra Neure und Verträglich -> 3 scales
extroversion <- c("bfi_e1", "bfi_e2", "bfi_e3", "bfi_e4", "bfi_e5", "bfi_e6", "bfi_e7", "bfi_e8")
neuroticism <- c("bfi_n1", "bfi_n2", "bfi_n3", "bfi_n4", "bfi_n5", "bfi_n6", "bfi_n7", "bfi_n8")
conscientiousness<- c("bfi_c1", "bfi_c2", "bfi_c3", "bfi_c4", "bfi_c5", "bfi_c6", "bfi_c7", "bfi_c8", "bfi_c9")

data_bfi_N_E_C <- data_raw_bfi_adjusted |>
  select(ID, extroversion, neuroticism, conscientiousness) |>
  rowwise()|>
  filter(!if_all(-ID, is.na)) |>
  mutate(exclude_impossible = if_else(all(c_across(c(extroversion, neuroticism, conscientiousness)) %in% 1:6), "include", "exclude"))|>
  mutate(exclude_not_completed = if_else(any(is.na(c_across(c(extroversion, neuroticism, conscientiousness)))), "exclude", "include"))



#Abgleich, ob alle IDs berücksichtigt worden sind und jeder ID entweder in NEC or AO ist

#179 Observationen wie im nicht merged Satz - heisst komplett
merged_data <- full_join(data_bfi_A_O, data_bfi_N_E_C, by = "ID")|>
  select("ID")
notmerged_data <- data_raw_bfi_adjusted|>
  select("ID")


differences_data1 <- anti_join(notmerged_data, merged_data, by = "ID")
differences_data2 <- anti_join(merged_data, notmerged_data, by = "ID")
#keine unterschiedlichen Daten gefunden!

#keine Dupilcate!
duplicated(merged_data)


```


## Mean score
- Mean-score the subscales of the BFI scale. Each participant only got either 2 or 3 subscales. 

 - Check that the mean scores do not violate the min and max possible score (i.e., first determine this min and max score), and revise your scoring code if it does. 
```{r}





```

# IAT Scale

## D Score
- Score the trial-level IAT data using the Greenwald "D" score: Calculate a mean RT ("mean1") for blocks 3 and 6 (one score using trials from both blocks), a mean RT ("mean2") for blocks 4 and 7 (one score using trials from both blocks), and the SD of RTs in blocks 3, 4, 6 and 7 ("SD"). To calculate D: D = (mean2 - mean1)/SD. Blocks 1, 2, and 5 are practice blocks and must be discarded. 
```{r}


```


- Include a sanity check: check that all D scores are in the range -2 to +2. If not, revise your implementation of the scoring code. 

```{r}


```

## Exclusions
  - Create an exclusion variable and set participants with incomplete trial level IAT data to "exclude". Specifically, IAT should have 120 trials on the critical test blocks (i.e., blocks 3, 4, 6 and 7). Trials on the other (practice) blocks can be discarded.
  
```{r}


```

  - Create an exclusion variable for IAT performance: set participants with >10% of the participants trials are < 300ms, or if their accuracy is < than 75%. Only use trials from the critical test blocks when computing these (i.e., blocks 3, 4, 6 and 7).

```{r}


```

# Combine BFI & IAT
- Combine the demographics, BFI, and IAT data into one data frame. This data frame should be one-row-one-participant. Both the mean scored and item level BFI data should be present in the dataset.
```{r}



```

# Master exclusions
- Create a master exclude variable from the individual exclude variables. 
```{r}



```

# Write to disk
- Save the processed data to the data/processed/ folder as "data_processed.csv". 
```{r}

# exists already
#dir.create("../data/processed/")

# save data
#write_csv(data_processed, "../data/processed/data_processed.csv")

```

# Codebook 

- Create a codebook for the processed data file that explains what each variable represents.

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv")



if(!file.exists("../data/processed/data_processed_codebook.xlsx")){
  codebook_template <- data.frame(variable = colnames(data_processed)) |>
    mutate(explanation = NA)

  write.xlsx(codebook_template, file = "../data/processed/data_processed_codebook.xlsx")
}

```



# Session info

```{r}

sessionInfo()

```


