---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Analysis"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

# set knit options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Dependencies

```{r}

library(tidyverse)
library(knitr)
library(kableExtra)
library(janitor)
library(scales)

library("ggExtra")
library("ggplot2")
library("viridis") 
library("ggsci")
library(ggrepel)
library(ggmagnify)
library(ggridges)
library(patchwork)


```

# Data

Load the processed data and apply the global exclusions.

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv")

data_processed_after_exclusions <- data_processed |>
  filter(exclude_participant == "include")

```

# Sample descriptives

## Sample size before exclusions

```{r}

data_processed |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("Whole sample" = 1)) |> # note that you can add header rows to tables like this. The "1" indicates the number of columns the header should span. The sum of these numbers must equal the number of columns or you'll get an error.
  kable_classic(full_width = FALSE)

```

## Sample size after exclusions

Sample used in subsequent analyses

```{r}

data_processed_after_exclusions |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("For analysis" = 1)) |>
  kable_classic(full_width = FALSE)

```

## Age

```{r}

data_processed_after_exclusions |>
  mutate(age = as.numeric(age)) |>
  summarise(Mean = mean(age, na.rm = TRUE),
            SD = sd(age, na.rm = TRUE)) |>
  mutate_all(.funs = janitor::round_half_up, digits = 1) |>
  kable() |>
  add_header_above(header = c("Age" = 2)) |>
  kable_classic(full_width = FALSE)

```

## Gender

```{r}

data_processed_after_exclusions |> 
  rename(Gender = gender) |>
  group_by(Gender) |> 
  summarise(n = n()) |> 
  mutate(Percent = paste0(round_half_up((n / sum(n)) * 100, 1), "%")) |>
  mutate(Gender = stringr::str_to_sentence(Gender)) |> # Change the case of the Gender variable so that it prints nicely
  kable() |>
  kable_classic(full_width = FALSE)

```

# Descriptives

Descriptive statistics and plots of the measures (excluding the demographics variables)

## Self-reported evaluations

### Descriptive stats

```{r}

# overall self-reported evaluations
dat_mean_ratings <- data_processed_after_exclusions |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# self-reported evaluations by gender category
dat_mean_ratings_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_mean_ratings,
          dat_mean_ratings_by_gender) |>
  select(Subset = group, Mean, SD, n) |> # select variables of interest, and rename one 
  mutate(Subset = stringr::str_to_sentence(Subset)) |> # Change the case of the Subset variable so that it prints nicely
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "Self-reported evaluations" = 3)) |>
  kable_classic(full_width = FALSE)

```

### Descriptive plot

```{r}

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation)) +
  geom_histogram(binwidth = 1,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("Mean self-reported evaluation") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(1, 7)) +
  theme(panel.grid.minor = element_blank())

```

## AMP evaluations

### Descriptive stats

\TODO add table of means, SDs, Ns

```{r}


# overall AMP scores
dat_AMP_means <- data_processed_after_exclusions |>
  summarise(Mean = mean(AMP_score, na.rm = TRUE),
            SD = sd(AMP_score, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# AMP Scores by gender category
dat_AMP_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(AMP_score, na.rm = TRUE),
            SD = sd(AMP_score, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_AMP_means,
          dat_AMP_by_gender) |>
  select(Subset = group, Mean, SD, n) |>
  mutate(Subset = stringr::str_to_sentence(Subset)) |>
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "AMP Scores" = 3)) |>
  kable_classic(full_width = FALSE)


```

### Descriptive plots

```{r}

ggplot(data_processed_after_exclusions, aes(x = AMP_score)) +
  geom_histogram(binwidth = 0.05,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("AMP score") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 10))

```

# Analyses & hypothesis tests

## Self-reported evaluations are correlated with evaluations on the AMP

### Plot

```{r}

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(y = AMP_score,
           x = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  ylab("AMP score") +
  xlab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

```

More complex plots:

#### Axial hisograms

Scatter plots with axial histograms using ggExtra: https://cran.r-project.org/web/packages/ggExtra/vignettes/ggExtra.html

\TODO add axial histograms to a scatter plot. Split both the scatter plot and the histograms by gender.

```{r}
#install.packages("ggExtra")

#I know ugly colours, but somewhat i like it :''D

p_all_gender <- ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, colour = gender)) +
  geom_point() +
     scale_colour_manual(values = c("female"="#996699","male" = "#777777","nonbinary" =  "#e89d97"))
MARG_all_gender <-ggMarginal(p_all_gender, groupColour = TRUE, groupFill = TRUE)
print(MARG_all_gender)

#FEMALE
data_p_a_e_female <- data_processed_after_exclusions |> 
  filter(gender == "female")

p_female_gender <- ggplot(data_p_a_e_female, aes(AMP_score, mean_evaluation, colour = gender)) +
  geom_point() +
  scale_colour_manual(values = "#996699")
MARG_p_female_gender <- ggMarginal(p_female_gender, groupColour = TRUE, groupFill = TRUE)
print(MARG_p_female_gender)

#MALE
data_p_a_e_male <- data_processed_after_exclusions |> 
  filter(gender == "male")

p_male_gender <- ggplot(data_p_a_e_male, aes(AMP_score, mean_evaluation, colour = gender)) +
  geom_point() +
  scale_colour_manual(values = "#777777")
MARG_p_male_gender <-ggMarginal(p_male_gender, groupColour = TRUE, groupFill = TRUE)
print(MARG_p_male_gender)

#NONBINÄRY
data_p_a_e_nb <- data_processed_after_exclusions |> 
  filter(gender == "nonbinary")

p_nb_gender <- ggplot(data_p_a_e_nb, aes(AMP_score, mean_evaluation, colour = gender)) +
  geom_point() +
  scale_colour_manual(values =  "#e89d97")
MARG_p_nb_gender <- ggMarginal(p_nb_gender, groupColour = TRUE, groupFill = TRUE)
print(MARG_p_nb_gender)



```

#### Labelled points

Label points using ggrepel: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html

\TODO Label the points in a scatter plot using their participant codes.

```{r}

#install.packages("ggrepel")
library(ggrepel)

#NONBINÄRY
p_label <- ggplot(data_p_a_e_nb, aes(AMP_score, mean_evaluation, label = subject)) +
  geom_point(color = "#7a064c")

p_label + geom_text_repel() + labs(title = "plot of nonbinarys")


#FEMALE - to many overlaps
p_f_label <- ggplot(data_p_a_e_female, aes(AMP_score, mean_evaluation, label = subject)) +
  geom_point(color = "#7a060a")

p_f_label + geom_text_repel() + labs(title = "plot of females")

#MALE - to many overlaps
p_m_label <- ggplot(data_p_a_e_male, aes(AMP_score, mean_evaluation, label = subject)) +
  geom_point(color = "#996699")

p_m_label + geom_text_repel() + labs(title = "plot of males")




```

#### Magnify areas

Magnify areas of your plot with ggmagnify: https://hughjonesd.github.io/ggmagnify/

\TODO Magnify an area of one of your scatter plots, eg where there are a lot of data points in a small area.

```{r}
#install.packages("ggmagnify", repos = c("https://hughjonesd.r-universe.dev", 
#                 "https://cloud.r-project.org"))

#FEMALE - to many overlaps

from <- c(xmin =0.75,xmax = 1, ymin = 1, ymax = 1.2)
# Names xmin, xmax, ymin, ymax are optional:
to <- c(0.25,0.75, 2,3)

p_f_label + geom_magnify(from = from, to = to)



```

### Test

\TODO 

## Self-reported evalautions differ between men and women
```{r}

#I don't know what test, so I did a t-test

data_p_e_without_nb <- data_processed_after_exclusions |>
    filter(gender == c("female", "male"))


t_test_result <- t.test(mean_evaluation ~ gender, data = data_p_e_without_nb)
print(t_test_result)

```
### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

```{r}

#Split Histogram
ggplot(data_processed_after_exclusions, 
       aes(x = mean_evaluation, group= gender, fill = gender)) +
  facet_grid(~gender)+
  geom_histogram(binwidth = 1) +
  labs(title = "Self-reported Evaluations by Gender",
       x = "Mean evaluation",
       y = "Frequency") +
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"))


#Split Violin
ggplot(data_processed_after_exclusions, 
       aes(y = mean_evaluation, x = gender, fill =gender)) +
  geom_violin(show.legend = FALSE) +
  labs(title = "Self-reported Evaluations by Gender",
       y = "Mean evaluation",
       x = "Gender")+
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"))


#raincloud plot
ggplot(data_processed_after_exclusions, aes(y = gender,x = mean_evaluation, fill = gender)) +
  geom_density_ridges(alpha = 0.7, scale = 0.5) +
  geom_point(position = position_jitter(), alpha = 0.5)+
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"))



```

### Test

\TODO 

```{r}

#???????????

```

## Evaluations on the Affect Misattribution Procedure differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

This time, vary the labeling and order of the legend, e.g., capitalise "Men" and "Women", and know how to change the order of the factors.

```{r}
#REARRANGE the order of the factors
data_p_a_e_rearranged <- data_processed_after_exclusions |> 
  mutate(gender = factor(gender, levels = c("nonbinary", "female", "male")))


#Split Histogram
ggplot(data_p_a_e_rearranged, 
       aes(x = AMP_score, group= gender, fill = gender)) +
  facet_grid(~gender)+
  geom_histogram(binwidth = 1) +
  labs(title = "AMP scores by Gender",
       x = "AMP Scores",
       y = "Frequency",
       fill = "Gender") +
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"),
                    breaks = c("nonbinary", "female",  "male"),  # Specify the order
                    labels=c("Nonbinary", "Women", "Men"))




#Split Violin 
ggplot(data_p_a_e_rearranged, 
       aes(y = AMP_score, x = gender, fill =gender)) +
  geom_violin() +
  labs(title = "Self-reported Evaluations by Gender",
       y = "AMP Scores",
       x = "Gender",
       fill = "Gender")+
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"),
                    breaks = c("nonbinary", "female",  "male"),  # Specify the order
                    labels=c("Nonbinary", "Women", "Men"))


#raincloud plot
ggplot(data_p_a_e_rearranged, aes(y = gender,x = AMP_score, fill = gender)) +
  geom_density_ridges(alpha = 0.7, scale = 0.5) +
  geom_point(position = position_jitter(), alpha = 0.5)+
  labs(title = "AMP scores by Gender",
       x = "AMP Scores",
       y = "Gender",
       fill = "Gender")+
  scale_fill_manual(values = c("female"="#996699","male" = "#777777","nonbinary" = "#e89d97"),
                    breaks = c("nonbinary", "female",  "male"),  # Specify the order
                    labels=c("Nonbinary", "Women", "Men"))



```

### Test

\TODO 

```{r}

#?????????

```

## Combining plots

Combine plots using patchwork: https://patchwork.data-imaginist.com/

\TODO Combine at least three of the above plots into one.

```{r}
#install.packages('patchwork')

#one varaiant
p_female_gender + p_male_gender + p_nb_gender

#other variant
(p_female_gender | p_male_gender | p_nb_gender)/
  p_all_gender

```

## Saving plots

Save plots to disk with `ggsave()`

\TODO Save the above combined plot to disk as both .png and .pdf. Ensure the png has at least 300dpi resolution.

```{r}

tosave<-(p_female_gender | p_male_gender | p_nb_gender)/
  p_all_gender



dir.create("../data/plots/")

ggsave("../data/plots/GENDERcomb_plot.png", plot = tosave, dpi = 300, device = "png")

ggsave("../data/plots/GENDERcomb_plot.pdf", plot = tosave, device = "pdf")


```

# Session info

```{r}

sessionInfo()

```



